---
title: "Crimes in Boston, Quick EDA with R "
author: Siyi Lin
date: June 6, 2019
output:
  md_document:
    variant: markdown_github
---

This is my coursework. Our group is wondering the crime in Boston area. We use the dataset from Kaggle, [Crime in Boston](https://www.kaggle.com/AnalyzeBoston/crimes-in-boston)

* What’s the dataset about?

This is a dataset containing records from the new crime incident report system in Boston area, which includes a reduced set of fields focused on capturing the type of incident as well as when and where it occurred.

* Which party collected the dataset?

Crime incident reports are provided by Boston Police Department (BPD) to document the initial details surrounding an incident to which BPD officers respond.

* Which period of time is covered?

June 14, 2015 to September 3, 2018


# Load Library

```{r}
library(tidyverse)
library(DataExplorer)
library(lubridate)
```


# Load Data

```{r}
Boston_Crime <- read.table("Boston_Crime.csv", header = TRUE, sep=",")
```


# Inspecting data frames

Use head() function to view the first few rows.
```{r}
head(Boston_Crime,5)
```


Use str() function to check the structure of the data
```{r}
str(Boston_Crime)
```


```{r}
summary(Boston_Crime)
```


Anthor way: to use glimpse() function to see every column in a data frame
```{r}
glimpse(Boston_Crime)
```


```{r}
plot_intro(Boston_Crime)
```




# Let's start the visualization and Exploratory Data Analysis (EDA)  

```{r}
plot_correlation(Boston_Crime)
```


```{r}
plot_histogram(Boston_Crime)
```


```{r}
plot_bar(Boston_Crime)
```



```{r}
Boston_Crime  %>% separate(OCCURRED_ON_DATE, c("Date", "Time"), sep = " ") %>% mutate(Date = ymd(Date)) %>% 
    ggplot(aes(Date))+
    geom_freqpoly() +
    ylab("Number of Crimes")
```




```{r}
Boston_Crime  %>% count(OFFENSE_CODE_GROUP) %>% arrange(-n) %>% head(30) %>% 
  ggplot(aes(reorder(OFFENSE_CODE_GROUP,n), n))+
  geom_col()+
  coord_flip()+
  labs(x = NULL, y = 'Counts')
```




```{r}
Boston_Crime %>% count(STREET) %>% arrange(-n) %>% head(15) %>% 
    ggplot(aes(reorder(STREET,n), n))+
    geom_col()+
    coord_flip()+
    labs(x = NULL, y = NULL)
```





```{r}
Boston_Crime %>% filter(DISTRICT %in% (Boston_Crime %>% count(DISTRICT) %>% arrange(-n) %>% pull(DISTRICT)),
                OFFENSE_CODE_GROUP %in% (Boston_Crime %>% count(OFFENSE_CODE_GROUP) %>% arrange(-n) %>% head(5) %>% pull(OFFENSE_CODE_GROUP))
                ) %>% 
    ggplot(aes(DISTRICT, fill = OFFENSE_CODE_GROUP))+
    geom_bar()+
    scale_fill_ordinal()+
    coord_flip()
```




```{r}
Boston_Crime %>% filter(STREET %in% (Boston_Crime %>% count(STREET) %>% arrange(-n) %>% head(5) %>% pull(STREET)),
                OFFENSE_CODE_GROUP %in% (Boston_Crime %>% count(OFFENSE_CODE_GROUP) %>% arrange(-n) %>% head(5) %>% pull(OFFENSE_CODE_GROUP))
                ) %>% 
    ggplot(aes(STREET, fill = OFFENSE_CODE_GROUP))+
    geom_bar(position = "fill")+
    scale_fill_ordinal()+
    coord_flip()
```



```{r}
Boston_Crime %>% filter(STREET %in% (Boston_Crime %>% count(STREET) %>% arrange(-n) %>% head(5) %>% pull(STREET))) %>% 
    ggplot(aes(DISTRICT, fill = STREET))+
    geom_bar(position = "fill")+
    coord_flip()+
    scale_fill_ordinal()
```





```{r}
Boston_Crime %>% filter(STREET %in% (Boston_Crime %>% count(STREET) %>% arrange(-n) %>% head(5) %>% pull(STREET))) %>% 
    ggplot(aes(DAY_OF_WEEK, fill = STREET))+
    geom_bar()+
    coord_flip()+
    scale_fill_ordinal()
```




```{r}
Boston_Crime %>% filter(OFFENSE_CODE_GROUP %in% (Boston_Crime %>% count(OFFENSE_CODE_GROUP) %>% arrange(-n) %>% head(5) %>% pull(OFFENSE_CODE_GROUP))) %>% 
    ggplot(aes(HOUR, fill = OFFENSE_CODE_GROUP))+
    geom_bar()+
    coord_flip()+
    scale_fill_ordinal()
```


```{r}
Boston_Crime %>% filter(OFFENSE_CODE_GROUP %in% (Boston_Crime %>% count(OFFENSE_CODE_GROUP) %>% arrange(-n) %>% head(5) %>% pull(OFFENSE_CODE_GROUP))) %>% 
  ggplot(aes(HOUR, fill = OFFENSE_CODE_GROUP))+
  geom_bar()+
  facet_wrap(~YEAR)+
  coord_flip()+
  scale_fill_ordinal()
```



```{r}
Boston_Crime %>% filter(OFFENSE_CODE_GROUP %in% (Boston_Crime %>% count(OFFENSE_CODE_GROUP) %>% arrange(-n) %>% head(5) %>% pull(OFFENSE_CODE_GROUP))) %>% 
  ggplot(aes(DISTRICT, fill = OFFENSE_CODE_GROUP))+
  geom_bar()+
  facet_wrap(~YEAR)+
  coord_flip()+
  scale_fill_ordinal()
```


# Resource

[ggplot cheatsheet](https://rstudio.com/wp-content/uploads/2016/11/ggplot2-cheatsheet-2.1.pdf)

[Introduction to Data Exploration and Analysis with R](https://bookdown.org/mikemahoney218/IDEAR/visualizing-your-data.html#diamonds)

[Kaggle Notebook - Crime in Boson EDA with R](https://www.kaggle.com/ekrembayar/crimes-in-boston-eda-with-r)

